Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-06-25 presentation/presentation.tex
[major] add final ppt for air2017

\begin{frame}[noframenumbering,label=main]{Outline}
	\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}
	\linespread{1.5}
	\begin{columns}[t]
		\begin{column}{0.65\textwidth}
			\begin{itemize}
				\item Clothing assistance is a basic and important assistance activity in the daily life of the elderly and disabled people
				\item Need of robotic clothing assistance is growing
			\end{itemize}
		\end{column}

		\begin{column}{0.35\textwidth}
			\begin{figure}
				\includegraphics[width=0.8\textwidth]{robotic_clothing_assistance}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\begin{block}{Major challenges involved}
		\begin{itemize}
			\item Close interaction of the robot with non-rigid clothing article
			\item Safe human-robot interaction
			\item Estimation of human-cloth relationship
		\end{itemize}
	\end{block}
\end{frame}

@@

	The system is defined as
	\vskip -1em
	\begin{equation*}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation*}
	\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep0.1em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}
	\vskip -0.6em
	\begin{exampleblock}{}
		$f$ is a function of \textit{canonical system}, denoted by $x$ as $\dot{x} = -\alpha_x x$
	\end{exampleblock}

@@

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\vskip-2.8em
	\begin{equation*}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation*}
	\vskip-0.5em
	{\small
		where:
		%\vskip-0.8em
		\begin{itemize}
			\setlength\itemsep{0.2em}
			\item $y_0$ is the initial state of the system
			\item $w_i$ is a weighting for a given basis function $\psi_i$
			\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
		\end{itemize}
	}
	\vskip-1em
	\begin{exampleblock}{Imitating a desired path}
		The desired forcing term $f$ which affects the system acceleration, is written as
		\vskip-1em
		\begin{equation*}
			\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
			\label{eq:imitate_f}
		\end{equation*}

		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-1em
		\begin{equation*}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation*}
	\end{exampleblock}
	\vskip-1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

@@

	\begin{figure}
		\includegraphics[width=0.9\textwidth]{images/imitate_path}
	\end{figure}
	\vskip-0.7em
	%\centering{
	\tiny{Back to \hyperlink{main}{\beamerbutton{main}}}
	%}
\end{frame}
\end{document}

>>>>

%\begin{frame}[noframenumbering,label=main]{Outline}
%	\tableofcontents
%\end{frame}

\section{Introduction}
\begin{frame}{Introduction}
	%\linespread{1.5}

	\vskip -2em
	\begin{columns}[t]
		\begin{column}{0.6\textwidth}
			\begin{itemize}
				\item Japan is a super-aging society
				\item In 2030, 1.8 person is supposed to care 1 elderly
				\item 400,000 care givers are lacking now
				\item Clothing is one of the most suffering daily activities for elderly
			\end{itemize}
		\end{column}

		\begin{column}{0.4\textwidth}
			\vskip -1em
			\begin{figure}
				\includegraphics[trim={4px 4px 4px 4px},clip,width=\textwidth]{japan_population}
				\caption{Japan population growth\footnotemark}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.7\textwidth}
			\begin{block}{Major challenges involved}
				\begin{itemize}
					\item Close interaction of the robot with cloth
					\item Safe human-robot interaction
					\item Estimation of human-cloth relationship
				\end{itemize}
			\end{block}
		\end{column}

		\begin{column}{0.25\textwidth}
			\begin{figure}
				\includegraphics[width=0.7\textwidth]{robotic_clothing_assistance}
			\end{figure}
		\end{column}
	\end{columns}

	\footcitetext{jonMcDonald2016japan}
\end{frame}

@@

	The system is defined as
	\vskip -1em
	\begin{equation*}
		\ddot{y} = \alpha \left( \beta \left(g - y\right) - \dot{y}\right) + f
		\label{eq:attractor_with_f}
	\end{equation*}
	%\begin{equation*}
	%	\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
	%	\label{eq:attractor_with_f}
	%\end{equation*}
	\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep0.1em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}
	\vskip -0.6em
	\begin{exampleblock}{}
		$f$ is a function of \textit{canonical system}%, denoted by $x$ as $\dot{x} = -\alpha_x x$
	\end{exampleblock}

@@

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\vskip-2.8em
	\begin{equation*}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation*}
	\vskip -0.5em
	{\small
		where:
		%\vskip-0.8em
		\begin{itemize}
			\setlength\itemsep{0.2em}
			\item $y_0$ is the initial state of the system
			\item $w_i$ is a weighting for a given basis function $\psi_i$
			\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
		\end{itemize}
	}
	\vskip -1em
	\begin{exampleblock}{Imitating a desired path}
		The desired forcing term $f$ which affects the system acceleration, is written as
		\vskip -1em
		\begin{equation*}
			\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
			\label{eq:imitate_f}
		\end{equation*}

		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip -1em
		\begin{equation*}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation*}
	\end{exampleblock}
	\vskip -1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

\begin{frame}{Example of DMP}
	\vskip -2em
	\begin{figure}
		\includegraphics[trim={0 15px 0 0},clip, width=0.9\textwidth]{DMP_BFs}
		\caption{\small{Effect of \textit{no. of basis functions}}}
	\end{figure}

	\vskip -2em
	\begin{figure}
		\includegraphics[trim={0 14px 0 20px},clip, width=0.9\textwidth]{DMP_Goal}
		\caption{\small{DMP adaptation to new goal \textit{(new goal = 1.5 * old goal)}}}
	\end{figure}
\end{frame}

@@

	\begin{figure}
		\includegraphics[width=0.9\textwidth]{images/imitate_path}
	\end{figure}
	\vskip -0.7em
	%\centering{
	\tiny{Back to \hyperlink{main}{\beamerbutton{main}}}
	%}
\end{frame}
\end{document}
